### 2019-05-06 paper-four/paper-four.tex
notes recorded for paper four

>>>>

\begin{itemize}
  \item Old students (Goenka; forward ref other methods of learning)
  \item People looking to deepen practice
  \item Meditators who haven't chosen a technique yet
\end{itemize}

\pagebreak

\begin{center}
  \Huge{Eka Maggo? Learning Vipassana Elsewhere}
\end{center}

\begin{itemize}
  \item Ledi Sayadaw: 5 hours a day anapana, ``hairs of the head and the body''
  \item Other students of U Ba Khin: ``The Quiet Mind'', ``Beyond the Breath''
  \item ``Vipassana'': sensations matter more than terminology (3-day course, 10-day course), other forms of ``Vipassana'' not of interest, Zazen
\end{itemize}

\pagebreak

\begin{center}
  \Huge{Concepts, Ideas, Help}
\end{center}

\begin{itemize}
  \item The Cheat Code: moving attention => sati vs. anicca
  \item Circle Awareness Drawing: how the 5 sense doors shut down
  \item Learn to sit cross-legged
\end{itemize}

\pagebreak

\begin{center}
  \Huge{Warnings}
\end{center}

\begin{itemize}
  \item This document itself is a hindrance
  \item Don't get bogged down by ``perfect objectivity'' or ``perfect equanimity'' - yes muscles and blood flow follow your attention
  \item Do not use meditation to get high
  \item Do not mix meditations (1. dangers, 2. meditation ``doing itself'' - anatta)
\end{itemize}
